---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# backends

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
<!-- badges: end -->

List of [DBI](https://dbi.r-dbi.org) backends.

```{r all-from-file, include = FALSE}
all_df <- jsonlite::fromJSON("docs/all.json", flatten = TRUE)
```

```{r all-url, echo = FALSE}
format_pkg <- function(name, version, title, description, date, maintainer, license, url, bugs) {
  
  if (length(url) > 0 && !anyNA(url)) {
    name <- paste0("[", name, "](", url[[1]], ")")
    url <- url[-1]
  }
  
  if (length(url) > 0 && !anyNA(url)) {
    url <- paste0(" [:link:](", url, ")", collapse = "")
  } else {
    url <- ""
  }
  
  if (!is.na(bugs)) {
    bugs <- paste0(" [:bug:](", bugs, ")")
  } else {
    bugs <- ""
  }
  
  paste0(
    "## ", name, " ", version, " (", date, ")", url, bugs, "\n\n",
    
    title, "\n\n",
    
    description, "\n\n",
    
    "Maintainer: ", maintainer, ". License: ", license, "\n\n"
  )
}

knitr::asis_output(purrr::pmap_chr(all_df, format_pkg))
```

# Implementation

The list of all known DBI backends is provided as a set of static JSON files.


## Usage

### Query all packages

```{r all, eval = FALSE}
all <- httr::GET("https://r-dbi.github.io/backends/all.json")
httr::stop_for_status(all)
all_df <- httr::content(all, flatten = TRUE, simplifyVector = TRUE)
```

### Query a single package

```{r single}
first_name <- all_df$name[[1]]
first_url <- paste0("https://r-dbi.github.io/backends/by-package/", first_name, ".json")
first <- httr::GET(first_url)
httr::stop_for_status(first)
httr::content(first)
```


## Updating the database

The database is updated via `script/prepare.R` which is run daily by GitHub Actions.
Existing packages are updated directly.
For new or removed packages, pull requests are opened.

---

Please note that the 'backends' project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
